---
title: "Project"
author: "David Suero Cobos"
date: "2022-12-05"
output: html_document
---
```{r}
#Loading libraries
library(dplyr)
library(ggplot2)
library(tidyverse)
```

# Project
## EDA - Exploratory Data Analysis
### Overview of the dataset
#### Goal
*Students enrolled in different undergraduate degrees*, such as agronomy, design,
education, nursing, journalism, management, social service, and technologies. 

The dataset includes information known at the time of *student enrollment* 
(academic path, demographics, and social-economic factors) and the *students'* 
*academic performance  at the end of the first and second semesters.* 

The data is used to build classification models to *predict students' dropout and* 
*academic sucess* by using machine learning techniques to identify students at 
risk at an early stage of their academic path. The problem is formulated as a 
three category classification task *(dropout, enrolled, and graduate)*, in which 
there is a strong imbalance towards one of the classes.

```{r}
Students <- read.csv("data.csv",sep = ";")
Students
# Summarizing of our data
summary(Students)
glimpse(Students) 
```

#### Variables that may raise questions
Elements that impact students in their decision to enrol, drop out or graduate.
1. Independent Variable: Target
- Marital status
- Application.order
- Course
- Daytime/evening attendance
- Previous qualification
- Previous qualification (grade)
- Nacionality
- Admission grade
- Displaced
- Educational special needs
- Debtor
- Tuition fees up to date
- Gender
- Scholarship holder
- Age at enrollment
- International
- Curricular units 1st sem (enrolled)
- Curricular units 1st sem (approved)
- Curricular units 1st sem (grade)
- Curricular units 2nd sem (enrolled)
- Curricular units 2nd sem (approved)
- Curricular units 2nd sem (grade)
- Unemployment rate
- GDP
- Pass rate (We will need to create this variable)

----------------
### Drop all variables that will not be used.
- Application.mode
- Mother's qualification
- Father's qualification
- Mother's occupation
- Father's occupation
- Curricular units 1st sem (credited)
- Curricular units 1st sem (evaluations)
- Curricular units 1st sem (without evaluations)
- Curricular units 2nd sem (credited)
- Curricular units 2nd sem (evaluations)
- Curricular units 2nd sem (without evaluations)
- Inflation rate
```{r}
Students <-  subset(Students, 
                    select = -c(Application.mode,
                                Mother.s.qualification, 
                                Father.s.qualification,
                                Mother.s.occupation, 
                                Father.s.occupation,
                                Curricular.units.1st.sem..credited.,
                                Curricular.units.1st.sem..evaluations.,
                                Curricular.units.1st.sem..without.evaluations.,
                                Curricular.units.2nd.sem..credited.,
                                Curricular.units.2nd.sem..evaluations.,
                                Curricular.units.2nd.sem..without.evaluations.,
                                Inflation.rate))
head(Students)
colnames(Students)
```

----------------
### Cleaning Variable names
This step is because there are variable names that are difficult to handle due 
to punctuation.
```{r}
Students <- Students %>% 
  rename(Previous.qualification.grade = Previous.qualification..grade.)

Students <- Students %>% 
  rename(Daytime.evening.attendance = Daytime.evening.attendance.)

Students <- Students %>% 
  rename(Curricular.units.1st.sem.enrolled = Curricular.units.1st.sem..enrolled.)

Students <- Students %>% 
  rename(Curricular.units.1st.sem.approved = Curricular.units.1st.sem..approved.)

Students <- Students %>% 
  rename(Curricular.units.1st.sem.grade = Curricular.units.1st.sem..grade.)

Students <- Students %>% 
  rename(Curricular.units.2nd.sem.enrolled = Curricular.units.2nd.sem..enrolled.)

Students <- Students %>% 
  rename(Curricular.units.2nd.sem.approved = Curricular.units.2nd.sem..approved.)

Students <- Students %>% 
  rename(Curricular.units.2nd.sem.grade = Curricular.units.2nd.sem..grade.)

names(Students)
```

----------------
### Renaming values of our variables
The purpose of this is to be able to correctly visualize the values that will be 
shown in the graphs that we will analyze later.
```{r}
library(stringr)
#Marital status
rep_str = c('1'='single',
            '2'='married',
            '3'='widower',
            '4'='divorced',
            '5'='facto union',
            '6'='legally separated')
Students$Marital.status <- str_replace_all(Students$Marital.status, rep_str)

#Application order
rep_str = c('1'='1st choice',
            '2'='2nd choice',
            '3'='3rd choice',
            '4'='4th choice',
            '5'='5th choice',
            '6'='6th choice',
            '7'='7th choice',
            '8'='8th choice',
            '9'='9th choice')
Students$Application.order <- str_replace_all(Students$Application.order, rep_str)


#Course
rep_str = c('33'='Biofuel Production Technologies',
            '171'='Animation and Multimedia Design',
            '8014'='Social Service (evening)',
            '9003'='Agronomy',
            '9070'='Communication Design',
            '9085'='Veterinary Nursing',
            '9119'='Informatics Engineering',
            '9130'='Equinculture',
            '9147'='Management (daytime)',
            '9238'='Social Service (daytime)', 
            '9254'='Tourism',
            '9500'='Nursing',
            '9556'='Oral Hygiene',
            '9670'='Advertising and Marketing Management',
            '9773'='Journalism and Communication',
            '9853'='Basic Education',
            '9991'='Management (evening)')
Students$Course <- str_replace_all(Students$Course, rep_str)

#Daytime/evening attendance
rep_str = c('1'='daytime','0'='evening')
Students$Daytime.evening.attendance <- 
  str_replace_all(Students$Daytime.evening.attendance, rep_str)
Students$Daytime.evening.attendance

#Previous qualification
rep_str = c('1'='Secondary education',
            '2'='Bachelors degree',
            '3'='Degree',
            '4'='Masters',
            '5'='Doctorate ',
            '6'='Frequency of higher education',
            '9'='Schooling',
            '10'='Schooling',
            '12'='Schooling',
            '14'='Schooling', 
            '15'='Schooling',
            '19'='Basic education',
            '38'='Basic education',
            '39'='Technological specialization course',
            '40'='Degree',
            '42'='Professional higher technical course',
            '43'='Master')
Students$Previous.qualification <-
  str_replace_all(Students$Previous.qualification, rep_str)
Students$Previous.qualification

#Nacionality
rep_str = c('1'='Portuguese',
            '2'='German',
            '6'='Spanish',
            '11'='Italian',
            '13'='Dutch',
            '14'='English',
            '17'='Lithuanian',
            '21'='Angolan',
            '22'='Cape Verdean',
            '24'='Guinean',
            '25'='Mozambican',
            '26'='Santomean',
            '32'='Turkish',
            '41'='Brazilian',
            '62'='Romanian',
            '100'='Moldova (Republic of)',
            '101'='Mexican',
            '103'='Ukrainian',
            '105'='Russian',
            '108'='Cuban',
            '109'='Colombian')
Students$Nacionality <- str_replace_all(Students$Nacionality, rep_str)

#Displaced
rep_str = c('1'='yes','0'='no')
Students$Displaced <- 
  str_replace_all(Students$Displaced, rep_str)

#Educational special needs
rep_str = c('1'='yes','0'='no')
Students$Educational.special.needs <- 
  str_replace_all(Students$Educational.special.needs, rep_str)

#Debtor
rep_str = c('1'='yes','0'='no')
Students$Debtor <- str_replace_all(Students$Debtor, rep_str)

#Tuition fees up to date
rep_str = c('1'='yes','0'='no')
Students$Tuition.fees.up.to.date <- 
  str_replace_all(Students$Tuition.fees.up.to.date, rep_str)

#Gender
rep_str = c('1'='male','0'='female')
Students$Gender <- str_replace_all(Students$Gender, rep_str)

#Scholarship holder
rep_str = c('1'='yes','0'='no')
Students$Scholarship.holder <- str_replace_all(Students$Scholarship.holder, rep_str)

#International
rep_str = c('1'='yes','0'='no')
Students$International <- str_replace_all(Students$International, rep_str)
```

----------------
### Transforming variables to factors
Most variables are discrete (Characters), so we must convert them to factors to 
avoid interpretation errors later on. 

However, there are some that have multiple variables, so it is not convenient to 
add them as factors. We will add only those that contain different categories 
to be able to reflect them in graphs.
```{r}
#We have to convert our discrete values to factor values
names <- c('Marital.status','Application.order','Course' ,
           'Daytime.evening.attendance','Previous.qualification',
           'Nacionality', 'Displaced' ,'Educational.special.needs','Debtor' ,
           'Tuition.fees.up.to.date','Gender' ,'Scholarship.holder',
           'International','Target')
Students[,names] <- lapply(Students[,names] , factor)
str(Students)
Students

```

----------------
### Errors in our factor levels
```{r}
library(plyr)

#Nacionality
levels(Students$Nacionality)
Students$Nacionality <- revalue(Students$Nacionality, c("3German"="German", "German4"="German", "GermanGerman"="German", "Portuguese05"="Portuguese", "Portuguese0Portuguese"="Portuguese","Portuguese7"="Portuguese", 
"SpanishGerman"="Spanish", "4Portuguese"="Portuguese", "GermanPortuguese"="German",
"Portuguese00"="Portuguese", "Portuguese08"="Portuguese", "Portuguese3"="Portuguese","PortuguesePortuguese"="Portuguese", "German5"="German",
"GermanSpanish"="Spanish","Portuguese03"="Portuguese","Portuguese09"="Portuguese",
"Portuguese4"="Portuguese"))
levels(Students$Nacionality)

#Previous qualification
levels(Students$Previous.qualification)
Students$Previous.qualification <- 
  revalue(Students$Previous.qualification,c("Degree8"="Degree",
"DegreeSchooling"="Degree", "Masters0"="Masters",
"MastersBachelors degree"="Masters", "MastersDegree"="Masters", 
"Secondary education0"="Secondary education",
"Secondary educationBachelors degree"="Bachelors degree",
"Doctorate "="Doctorate",
"Secondary educationDoctorate "="Doctorate",
"Secondary educationMasters"="Masters", 
"Secondary educationSchooling"="Secondary education"))
levels(Students$Previous.qualification)
```

----------------
### Step 3: Cleaning the dataset, NAs, and inconsistent data
```{r}
(sum(is.na(Students))/
  (nrow(Students)*ncol(Students)))*100 #NAs

library(psych)
describe(Students)
```
We can observe that the dataset does not offer NA Values. Moreover, all the 
values in our dataset represent real values, so there are no errors in the data 
set, i.e., no inconsistent data.

### Creation of a new variable (Pass rate)
It would be good to analyze the pass rate of all students, so we will create a 
new variable to analyze it in detail later.
```{r}
Students

Students$Pass.rate.1st.sem <-
  Students$Curricular.units.1st.sem.approved/Students$Curricular.units.1st.sem.enrolled

Students$Pass.rate.2nd.sem <-
  Students$Curricular.units.2nd.sem.approved/Students$Curricular.units.2nd.sem.enrolled
```

----------------
### Studying our variables
*Possible variables that could influence others:*
FORMULAR PREGUNTAS PRIMERO A RAIZ DE ESTAS VARIABLES.
Elements that impact students in their decision to enrol, drop out or graduate.

#### Discrete varaiables
1. Independent Variable: *Target* 
- Marital status
```{r}
Marital.status.Graph <- ggplot(Students, aes(Marital.status,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Marital Status") + labs(color = "Target: ") + 
  ggtitle('Marital status / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Marital.status.Graph
#There seems to be a close relationship between the abandonment rate and 
#legal separation.
#On the other hand, the opposite is true for singles. They are those who have a 
#higher graduation rate
```

*- Application.order*
```{r}
Application.order.Graph <- ggplot(Students, aes(Application.order,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Application Order") + labs(color = "Target: ") +
  ggtitle('Application Order / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Application.order.Graph
#There seems to be a close relationship between the graduate rate and 
#the first poisition in the application order. This seems coherent, since those 
#who applied to their course in first position, are the ones who have more 
#interest in the subject.
#In the others, there is no aspect to highlight.
```

*- Course*
```{r}
Course.Graph <- ggplot(Students, aes(Course,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Course") + labs(color = "Target: ") +
  ggtitle('Course / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Course.Graph
#There seems to be a close relationship between the graduate rate and 
#the nursing degree, social service, journalism and Communication Design

#On the other side, there seems to be a close relationship between the Dropout 
#rate and the Biofuel Production Technologies, Equinculture, and Informatics
#Engineering
```

*- Daytime/evening attendance*
```{r}
Daytime.evening.attendance.Graph <- 
  ggplot(Students, aes(Daytime.evening.attendance,fill=Target)) + 
  geom_bar(position = "fill") + ylab("Proportion") + 
  xlab("Daytime Evening Attendance") + labs(color = "Target: ") +
  ggtitle('Daytime Evening Attendance / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Daytime.evening.attendance.Graph

#There seems to be a close relationship between the evenings and the droputs,
#maybe it´s beacuse people are more socially active in the afternoon, get 
#frustrated, and drop out of school.
```

*- Previous qualification* 
```{r}
Previous.qualification.Graph <- ggplot(Students, aes(Previous.qualification,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Previous Qualification") + labs(color = "Target: ") +
  ggtitle('Previous Qualification / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Previous.qualification.Graph

#Through this graph (and with the exception of the variable "Schoolarship" 
#which is mandatory for everyone), we can see how those careers with the highest 
#dropout rate are the doctorates and bachelors degree, and those with the lowest 
#dropout rate and the highest graduates, the master's degrees.
```

*- Nacionality*
```{r}
Nacionality.Graph <- ggplot(Students, aes(Nacionality,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Nacionality") + labs(color = "Target: ") +
  ggtitle('Nacionality / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Nacionality.Graph

#There seems to be a close relationship between the droputs and the portuguese
#people, and the graduate and german people.
```

*- Displaced*
```{r}
Displaced.Graph <- ggplot(Students, aes(Displaced,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Displaced") + labs(color = "Target: ") +
  ggtitle('Displaced / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Displaced.Graph

#There seems to be a close relationship between the droputs and the people
#who has not had to travel for his studies, same as the graduates with those same
#people. This may be due to the fact that international students generally know 
#that their conditions are more difficult,so they make more of an effort.
```

*- Educational special needs*
```{r}
Educational.special.needs.Graph <- ggplot(Students, aes(Educational.special.needs,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Educational Special Needs") + labs(color = "Target: ") +
  ggtitle('Educational Special Needs / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Educational.special.needs.Graph

#There´s no difference
```

*- Debtor*
```{r}
Debtor.Graph <- ggplot(Students, aes(Debtor,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Debtor") + labs(color = "Target: ") +
  ggtitle('Debtor / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Debtor.Graph

#There seems to be a close relationship between the droputs and debtors.
#This make sense since those who cannot afford to pay for their studies must 
#abandon their careers
```

*- Tuition fees up to date*
```{r}
Tuition.fees.up.to.date.Graph <- 
  ggplot(Students, aes(Tuition.fees.up.to.date,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Tuition fees up to date") + labs(color = "Target: ") +
  ggtitle('Tuition fees up to date / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Tuition.fees.up.to.date.Graph
#This, as in the previous case, makes sense, since they are considered debtors 
#and therefore, they will probably be expelled or will end up abandoning their 
#careers because they cannot afford them.
```

*- Gender*
```{r}
Gender.Graph <- ggplot(Students, aes(Gender,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Gender") + labs(color = "Target: ") +
  ggtitle('Gender / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Gender.Graph

#There is a big difference between the different genres. It can be explained by 
#the fact that women are generally much more responsible and hardworking than men.
```

*- Scholarship holder*
```{r}
Scholarship.holder.Graph <- ggplot(Students, aes(Scholarship.holder,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("Scholarship Holder") + labs(color = "Target: ") +
  ggtitle('Scholarship Holder / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Scholarship.holder.Graph

#This variable also makes sense, because generally, those students who receive 
#tuition, make a much greater effort to succeed in their careers, as it is a 
#good opportunity for them.
```

*- International*
```{r}
International.Graph <- ggplot(Students, aes(International,fill=Target)) + 
  geom_bar(position = "fill")  + 
  ylab("Proportion") + xlab("International") + labs(color = "Target: ") +
  ggtitle('International / Target') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
International.Graph

#There is no major difference
```

----------------
#### Continuous Variables -> 
Finally, we must compare our target variable with some continuous variables
which we will see below.

*- Courses / Previous qualification Grade*
```{r}
Previous.qualification.grade.Graph <- 
  ggplot(Students, aes(Course,Previous.qualification.grade,fill=Target)) + 
  geom_boxplot() + 
  ylab("Previous qualification Grade") + xlab("Courses") +
  ggtitle('Courses / Previous qualification Grade') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Previous.qualification.grade.Graph

#Through the continuous variable "Previous qualification Grade", and linking this 
#with the discrete variables "Target" and "Course" we can see how in practically 
#all courses, the Previous qualification Grade is lower in those students who 
#dropped out, which makes sense.

#The Agronomy course is the one with the highest difference
```

*- Courses / Admission grade*
```{r}
Admission.grade.Graph <- 
  ggplot(Students, aes(Course, Admission.grade, fill=Target)) + 
  geom_boxplot()  + 
  ylab("Admission grade") + xlab("Courses") + labs(color = "Target: ") +
  ggtitle('Courses / Admission grade') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Admission.grade.Graph

#As for the admission grade variable, we can see that the courses with the 
#highest admission grade rate are the same as those analyzed in the previous 
#section (Previous qualification Grade), which makes sense because the courses 
#establish their admission grade according to student demand, so if the admission 
#grade is high, so will be the grades that belong to the students of that course.
```

*- Courses / Age at enrollment*
```{r}
Age.at.enrollment.Graph <- 
  ggplot(Students, aes(Course, Age.at.enrollment, fill=Target)) + 
  geom_boxplot()  + 
  ylab("Age at enrollment") + xlab("Courses") + labs(color = "Target: ") +
  ggtitle('Courses / Age at enrollment') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Age.at.enrollment.Graph

#As for the age of the individuals in the different training courses, we can see 
#that the one with the highest average age is Social Service, followed by Management. 
#All the others are more or less in the same age range.

#As for the difference in our Target variable, it is clear that those who are 
#older have a much higher dropout rate than young people.
```

*- Courses / Curricular Units Approved 1st Semester*
```{r}
Curricular.units.1st.sem.approved.Graph <- ggplot(Students, aes(Course, Curricular.units.1st.sem.approved,fill=Target)) + 
  geom_boxplot()  + 
  ylab("Curricular Units Approved 1st Semester") + xlab("Courses") + 
  labs(color = "Target: ") +
  ggtitle('Courses / Curricular Units Approved 1st Semester') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Curricular.units.1st.sem.approved.Graph

#The graph shows that almost all courses follow the same trend, with the 
#exception of "Informatics Engineering", which has a lower number of approvals
#than the rest.

#Unsurprisingly, students who dropped out of the courses had a lower number of 
#approvals.
```

*- Courses / Pass Rate First Semester*
```{r}
Pass.rate.1st.sem.Graph <- 
  ggplot(Students, aes(Course,Pass.rate.1st.sem,fill=Target)) + 
  geom_boxplot()  + 
  ylab("Pass Rate First Semester") + xlab("Courses") + 
  labs(color = "Target: ") +
  ggtitle('Courses / Pass Rate First Semester') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Pass.rate.1st.sem.Graph

#As is logical, the graph shows that all of those graduates passed all of their 
#subjects (located in the upper part of the graph, in the 100% zone), while those
#who dropped out are at different lower rates.

#The course with the lowest pass rate is "Informatics Engineering", as we showed 
#in the previous step of number of passes, which makes sense because they are 
#related variables.
```

*- Courses / 1st Semester Grade*
```{r}
Students
Curricular.units.1st.sem.grade.Graph <- ggplot(Students, aes(Course, Curricular.units.1st.sem.grade,fill=Target)) + 
  geom_boxplot()  + 
  ylab("1st Semester Grade") + xlab("Courses") + 
  labs(color = "Target: ") +
  ggtitle('Courses / 1st Semester Grade') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Curricular.units.1st.sem.grade.Graph
#Once again, the graph shows that those students who completed their courses 
#had a higher final grade than those who dropped out.

#In addition, we can observe that the course with the highest final grade is 
#"Veterinary Nursing", while the one with the lowest grade is "Management".
```

*- Courses / Curricular Units Approved 2nd Semester*
```{r}
Curricular.units.2nd.sem.approved.Graph <- ggplot(Students, aes(Course, Curricular.units.2nd.sem.approved,fill=Target)) + 
  geom_boxplot()  + 
  ylab("Curricular Units Approved 2nd Semester") + xlab("Courses") + 
  labs(color = "Target: ") +
  ggtitle('Courses / Curricular Units Approved 2nd Semester') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Curricular.units.2nd.sem.approved.Graph

#As for the subjects with the highest number of passes in the second semester, 
#we have "Oral Hygiene", while the one with the lowest number of passes is 
#"Informatics Engineering" (as in the first semester).

#Once again, the rule is fulfilled that those students who graduated obtained 
#higher passes than those who dropped out.
```

*- Courses / Pass Rate 2nd Semester*
```{r}
Pass.rate.2nd.sem.Graph <- ggplot(Students, aes(Course, Pass.rate.2nd.sem,fill=Target)) + 
  geom_boxplot()  + 
  ylab("Pass Rate 2nd Semester") + xlab("Courses") + 
  labs(color = "Target: ") +
  ggtitle('Courses / Pass Rate 2nd Semester') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Pass.rate.2nd.sem.Graph

#As for the pass rate, the same happens as in the first semester, all the 
#graduates passed all their subjects, and the subject with the highest pass 
#rate is "Oral Hygiene", having already been analyzed in the previous step 
#(Number of passes). 
```

*- Courses / 2nd Semester Grade*
```{r}
Curricular.units.2nd.sem.grade.Graph <- ggplot(Students, aes(Course, Curricular.units.2nd.sem.grade,fill=Target)) + 
  geom_boxplot()  + 
  ylab("2nd Semester Grade") + xlab("Courses") + 
  labs(color = "Target: ") +
  ggtitle('Courses / 2nd Semester Grade') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Curricular.units.2nd.sem.grade.Graph

#As for the final grade of the second semester, it is curious to see how those 
#who passed the subject of "Informatics Engineering", were those who achieved a 
#better grade with respect to the other subjects.
```

*- Courses / Unemployment rate*
```{r}
Unemployment.rate.Graph <- ggplot(Students, aes(Course, Unemployment.rate,fill=Target)) + 
  geom_boxplot()  + 
  ylab("Unemployment rate") + xlab("Courses") + labs(color = "Target: ") +
  ggtitle('Courses / Unemployment rate') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
Unemployment.rate.Graph
#From the graph we can see how the unemployment rate has no influence at all on 
#the performance of students, neither of graduates nor of those who had to drop out.
```

*- Courses / GDP*
```{r}
GDP.Graph <- ggplot(Students, aes(Course, GDP,fill=Target)) + 
  geom_boxplot()  + 
  ylab("GDP") + xlab("Courses") + labs(color = "Target: ") +
  ggtitle('Courses / GDP') +
  theme(plot.title = element_text(hjust = 0.5,  face = "bold")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
GDP.Graph

#Similarly, GDP does not influence the performance of students, neither of 
#graduates nor of those who had to drop out.
```

--------------------------------------------------------------------------------
## Inferential statistics - Logistic regression
```{r}
library(ISLR)
logit <- glm(Target ~ ., data = Students, family = binomial(link = 'logit'))
summary(logit)
Students
```

As expected, not all variables are related to our target, as they are not 
statistically significant, therefore, we will only keep those that show certain 
relationship
```{r}
logit <- glm(Target ~ Course + Application.order + Marital.status +
            Previous.qualification, data = Students, 
            family = binomial(link = 'logit'))
summary(logit)
```


**PENDING**
